\chapter{Introduction}
\label{chapter: introduction}

% brief introduction explaining document contents
\section{About this lab assignment}

\paragraph{}
This document contains the report of the work carried out in this lab assignment. It is related with Logical Satisfiability and Heuristic Search. There are two main parts for this lab assignment, that are organized as follows:

\begin{itemize}
	\item Part 1 deals with the modelling of a parking problem, similar to the famous board game Rush Hour, by solving it as a SAT problem. This part has been implemented using Java and JACoP, a library for constraint programming.
    
	\item Part 2 deals with determining the necessary sequence of movements to reconfigure the parking into a different configuration given. This is solved using the heuristic search algorithm A*.
    
\end{itemize}

\section{Document contents}

\paragraph{}
This document has been divided in four chapters, following the format requested by our professor. The following list explains what does each chapter show:

\begin{itemize}
	\item Chapter \ref{chapter: introduction} (this one) explains the contents of the document. It serves as a reference for rapid lookup across this report.
    
	\item In chapter \ref{chapter: models description}, the models of the two proposed problems are discussed.
    
	\item Chapter \ref{chapter: analysis of results} analyzes the solutions yielded both for Part 1 and Part 2 problems. 

	\item Chapter \ref{chapter: conclusions} explains the difficulties we have faced while completing this lab assignment, both from a technical and a conceptual standpoint. It also describes what have we learned (or remembered) thanks to this lab assignment.
	
\end{itemize}
