\chapter{Models Description}
\label{chapter: models description}








%----------------------------------------- PART 1 --------------------------------------------------

\section{Part 1: SAT verification of the parking configuration}

\paragraph{}
For this part we had to refrain ourselves from the temptation of modelling the
problem as an assignment of cars to park positions, since these positions were
already fixed. Instead, we have to somehow \textit{check} that an (already
present) assignment was correct. In other words, the configuration read from the
input file should not be changed; JaCoP should not decide which values to assign
to the boolean variables that describe the parking. We have to make these values
\textit{fixed}, expressing this with propositional logic. One way we thought to
solve this problem is to include this information as disjunctions of only one
literal, and adding each one them to the CNF with a conjunction.


\subsection{Variables}

\paragraph{}
Variables have been defined as follows:
\begin{itemize}
  \item $c_{ij}$: there is a car at lane $i$ and position $j$
  \item $b^{d)}_{ij}$: car adjacent to that at $i,j$ entered the lane before
  \item $s^{d)}_{ij}$: car adjacent to that at $i,j$ has a category with the same waiting time
  \item $l^{d)}_{ij}$: car adjacent to that at $i,j$ has a category with lower waiting time
\end{itemize}
Where $d \in {L,R}$. $L$ represents information about the adjacent car at the left of car at $i,j$, and $R$ represents information about the adjacent car at the right of car at $i,j$.

\subsection{Propositional formula}

\paragraph{}
The formula can be divided in two parts: the part that checks for blocked cars, and the part that represents the parking configuration by using 1-variable clauses. It should be noticed that literals in the formula may be non-negated ($b^L_{ij}$) or negated ($\neg b^d_{ij}$), depending on the input file configuration. Since it would be incorrect to include a single formula (as literals on the right are non-negated or negated depending on the input file), the following equation represents a group of formulas, hence the use of set notation for the right part.

\paragraph{}
Therefore we get the following propositional formula:
\begin{equation}
  \bigand{\substack{i \in N,\\ j \in (0, N-1)}}l^{L)}_{ij} \lor (s^{L)}_{ij} \land b^{L)}_{ij}) \lor l^{R)}_{ij} \lor l^{R)}_{ij} \lor (s^{R)}_{ij} \lor b^{R)}_{ij})
  \bigand{\substack{
      \alpha \in\\
      B^{L)} \cup
      B^{R)} \cup \\
      S^{L)} \cup
      S^{R)} \cup \\
      L^{L)} \cup
      L^{R)} \cup \\
      C
    }}
    \alpha
\end{equation}
where
\begin{itemize}
  \item $B^{L)}$: matrix containing literals $b^{L)}_{ij}$ or $\neg b^{L)}_{ij}$ as loaded from the input file
  \item $S^{L)}$: matrix containing literals $s^{L)}_{ij}$ or $\neg s^{L)}_{ij}$ as loaded from the input file
  \item $S^{R)}$: matrix containing literals $s^{R)}_{ij}$ or $\neg s^{R)}_{ij}$ as loaded from the input file
  \item $L^{L)}$: matrix containing literals $l^{L)}_{ij}$ or $\neg l^{L)}_{ij}$ as loaded from the input file
  \item $L^{R)}$: matrix containing literals $l^{R)}_{ij}$ or $\neg l^{R)}_{ij}$ as loaded from the input file
  \item $C$: matrix containing literals $c_{ij}$ or $\neg c_{ij}$ as loaded from the input file
\end{itemize}

\paragraph{}
Turning this formula into CNF we get the following:
\begin{equation}
  \bigand{\substack{i \in N,\\ j \in (0, N-1)}}
  (l^{L)}_{ij} \lor l^{R)}_{ij} \lor s^{L)}_{ij} \lor s^{R)}_{ij}) \land
  (l^{L)}_{ij} \lor l^{R)}_{ij} \lor s^{L)}_{ij} \lor b^{R)}_{ij}) \land
  (l^{L)}_{ij} \lor l^{R)}_{ij} \lor s^{R)}_{ij} \lor b^{L)}_{ij}) \land
  (l^{L)}_{ij} \lor l^{R)}_{ij} \lor b^{L)}_{ij} \lor b^{R)}_{ij})
  \bigand{\substack{
      \alpha \in\\
      B^{L)} \cup
      B^{R)} \cup \\
      S^{L)} \cup
      S^{R)} \cup \\
      L^{L)} \cup
      L^{R)} \cup \\
      C
    }}
    \alpha
\end{equation}

\paragraph{}
Notice that the formula does not check literals related to the sides of the parking lot, since these are never going to be blocked.

%----------------------------------------- PART 2 --------------------------------------------------

\section{Part 2: Heuristic Search}

\paragraph{}
In this problem we are asked to move cars in a parking with an initial
configuration to get to a final configuration given. Cars can only perform
specific moves.

For solving this problem, we have used a Python3 implementation of the well-known
A* algorithm. This is an algorithm of heuristic search. In the following
sections the model and parameters used are explained.

\subsection{States}

\paragraph{}
We have decided to use parking configurations as states for the A* heuristic
search algorithm.
Each state of the problem is a different configuration of the cars in the parking
provided.

States are implemented as a class 'State', which includes a parking
configuration, a reference to its parent node, H value and G value.


\subsection{Operators}

\paragraph{}
When expanding a node, we calculate all the possible movements of the cars in
the parking. For each possible movement of each car, one node is generated. This
node contains the map after each movement. This is done by 'children' function,
that returns the child nodes after expanding a given node.

We want to point that only one movement of one car is allowed in a state change.

Also, each movement has associated a cost for performing it following the
statement requirements. When a operator is used, the cost (G) is saved.

\subsection{Initial state}

\paragraph{}
The initial state corresponds to the initial configuration of the parking
(a.k.a. first input file).
We save the data of this file in a matrix of Car objects.

\subsection{Final state}

\paragraph{}
The final state corresponds to the final configuration of the parking
(a.k.a. second input file).


\subsection{Heuristic function}

\paragraph{}
We have used Manhattan distance as the heuristic function. The distance is based
on a strictly horizontal and/or vertical path. This is based on the sum of each
distance of the current position of each car to its final position (H value).
